Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-21 paper/paper.tex
punctuation in intro

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
                        % id of corresponding address, if any
%   noteref={n1},                        % id's of article notes, if any
   email={vincent.lostanlen@nyu.edu}            % email address
]{\inits{VL}\fnm{Vincent} \snm{Lostanlen}}
\author[
   addressref={aff2},
   email={christian.elhajj@ls2n.fr}
]{\inits{CE}\fnm{Christian} \snm{El-Hajj}}
\author[
   addressref={aff3},
   email={mathias.rossignol@lonofi.com}
]{\inits{MR}\fnm{Mathias} \snm{Rossignol}}
\author[
   addressref={aff3},
   email={gregoire.lafay@lonofi.com}
]{\inits{GL}\fnm{Gr\'egoire} \snm{Lafay}}
\author[
   addressref={ccm},
   email={janden@flatironinstitute.org}
]{\inits{JA}\fnm{Joakim} \snm{And\'en}}
\author[
  corref={aff2},
  addressref={aff2},
  email={mathieu.lagrange@ls2n.fr}
]{\inits{ML}\fnm{Mathieu} \snm{Lagrange}}

@@

\address[id=aff1]{%                           % unique id
  \orgname{Music and Audio Research Lab, New York University}, % university, etc
  \street{370 Jay Street},                     %
  %\postcode{}                                % post or zip code
  \city{New York, NY},                              % city
  \cny{USA}                                    % country
}
\address[id=aff2]{%
  \orgname{LS2N, CNRS, Centrale Nantes, Nantes University},
  \street{1, rue de la Noe},
  \postcode{44000},
  \city{Nantes},
  \cny{France}
}
\address[id=aff3]{%
  \orgname{Lonofi},
  \street{57 rue Letort},
  \postcode{75018},
  \city{Paris},
  \cny{France}
}
\address[id=ccm]{%
  \orgname{Center for Computational Mathematics, Flatiron Institute},
  \street{162 5th Avenue},
  \city{New York, NY 10010},
  \cny{USA}
}

@@

\begin{artnotes}
%\note[id=n1]{Equal contributor}
\end{artnotes}

@@

Music information retrieval operates at either of two levels: symbolic and auditory \cite{downie2003mir}.
By resting on a notation system, the symbolic level facilitates the comparison of musical notes in terms of quantitative attributes, such as duration, pitch, or intensity at the source.
Timbre, in contrast, is a qualitative attribute of music, thus irreducible to a one-dimensional axis \cite{siedenburg2019chapter}.
As a result, symbolic representations describe timbre indirectly, either via visuotactile metaphors (\eg{} bright, rough, and so forth \cite{faure1996icmpc}) or via an instrumental playing technique (\eg{} bowed or plucked \cite{kostka2016book}).

@@

@@

Following the above discussed matters, we propose a ranking system that is based on a processing pipeline made of two main components, see Figure \ref{fig:pipeline}. The first component projects the audio signal of the query and the items of the database in a high dimensional timbre space using the scattering transform. The second component modify the timbre space by taking into account perceptual judgments represented as a consensus clustering of the items in the dataset, as presented in Section \ref{sec:judgments}. It considers the large margin nearest neigbors to learn the weights of the reprojection.

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/xp2example1.png}
\caption{Spatial and group organization provided by subject 1\footnote{The organizations of the other subjects are available online \url{https://mathieulagrange.github.io/paperPlayingTechniquesSimilarityLearning/demo}. For each subject, the stimuli can be played back by hovering on the dots.}.}
\label{fig:xp2display}
\end{figure}

In this study, we choose to condition the space using the aggregate similarity judgments given by several subjects. We found that using a hypergraph partitioning algorithm \cite{kernighan1970efficient,han1997scalable,strehl2002cluster} to produce the consensus similarity matrix performed well.

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/consensusVsI.png}
\caption{Normalized similarity matrix of the consensus clustering aggregated by the musical instruments used. Ordering is chosen to maximize readability.}
\label{fig:consensusVsI}
\end{figure}

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/consensusVsPt.png}
\caption{Normalized similarity matrix of the consensus clustering aggregated by the playing techniques used. Ordering is chosen to maximize readability.}
\label{fig:consensusVsPt}
\end{figure}

>>>>

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   noteref={n1},                        % id's of article notes, if any
   email={email@example.com}            % email address
]{\inits{VL}\fnm{Vincent} \snm{Lostanlen}}
\author[
   addressref={aff2},
   email={email@example.com}
]{\inits{CE}\fnm{Christian} \snm{El-Hajj}}
\author[
   addressref={aff2},
   email={email@example.com}
]{\inits{MR}\fnm{Mathias} \snm{Rossignol}}
\author[
   addressref={aff2},
   email={email@example.com}
]{\inits{GL}\fnm{Gr\'egoire} \snm{Lafay}}
\author[
   addressref={ccm},
   email={janden@flatironinstitute.org}
]{\inits{JA}\fnm{Joakim} \snm{And\'en}}
\author[
   addressref={aff2},
   email={email@example.com}
]{\inits{ML}\fnm{Mathieu} \snm{Lagrange}}

@@

\address[id=aff1]{%                           % unique id
  \orgname{Music and Audio Research Lab, New York University}, % university, etc
  \street{370 Jay Street},                     %
  %\postcode{}                                % post or zip code
  \city{New York, NY},                              % city
  \cny{USA}                                    % country
}
\address[id=aff2]{%
  \orgname{Marine Ecology Department, Institute of Marine Sciences Kiel},
  \street{D\"{u}sternbrooker Weg 20},
  \postcode{24105}
  \city{Kiel},
  \cny{Germany}
}
\address[id=ccm]{%
  \orgname{Center for Computational Mathematics, Flatiron Institute},
  \street{162 5th Avenue},
  \city{New York, NY 10010},
  \cny{USA}
}

@@

\begin{artnotes}
\note[id=n1]{Equal contributor}
\end{artnotes}

@@

Music information retrieval operates at either of two levels: symbolic and auditory \cite{downie2003mir}.
By resting on a notation system, the symbolic level facilitates the comparison of musical notes in terms of quantitative attributes, such as duration, pitch, or intensity at the source.
Timbre, in contrast, is a qualitative attribute of music, thus irreducible to a one-dimensional axis \cite{siedenburg2019chapter}.
As a result, symbolic representations describe timbre indirectly: either via visuotactile metaphors (\eg{} bright, rough, and so forth \cite{faure1996icmpc}) or via an instrumental playing technique (\eg{} bowed or plucked \cite{kostka2016book}).

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/xp2example1.png}
\caption{Spatial and group organization provided by subject 1.}
\label{fig:xp2display}
\end{figure}

It may also be of interest to condition the space using the aggregate similarity judgments given by several subjects. We found that using a hypergraph partitioning algorithm \cite{kernighan1970efficient,han1997scalable,strehl2002cluster} to produce the consensus similarity matrix performed well.

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/consensusVsI.png}
\caption{}
\label{fig:consensusVsI}
\end{figure}

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/consensusVsPt.png}
\caption{ }
\label{fig:consensusVsPt}
\end{figure}

@@

\ml{introduce the system globally, while stressing the ability of the system to be conditioned for one or many people (VL). consensus ou un compositeur particulier.}

@@
